Deep learning for geophysics

### 2024-06-02 manuscript.tex
Adjust sentiment in thesis abstract

The second topic explores a method for learning a representation of a potential field extent from scattered real-world survey data by a contemporary neural network.
The data-driven approach can extract high-resolution grids from the learned representation, as well as calculate analytical spatial gradients.
Grid rasters and horizontal gradients calculated with the method very closely match their numerical counterparts, however, vertical gradients do not.

>>>>

The second topic explores a method for learning a representation of a potential field extent from scattered real-world survey data by a contemporary neural network.
The data-driven approach can extract high-resolution grids from the learned representation, as well as calculate analytical spatial gradients.
Grid rasters and horizontal gradients calculated with the proposed method closely match their numerical counterparts from existing methods, presenting exciting avenues for further work in neural networks for geophysics.
